DLISA: Distributed Learning-based \\ Intelligent Service Agents

### 2014-11-28 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

@@

\section{The Model}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations. Each row shows the gain the community can achieve by collaborating with other 5 communities. In this example for community $\textless 348 \textgreater$ we have: \\
$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and would contain community $\{\textless1934, 2117\textgreater\}$.

>>>>

The rest of the paper is organized as follows. In Section 2 we briefly describe the preliminaries, discusses the web service community architecture, and the considered parameters in our feature vectors. Section 3 presents our solution model, the way data is trained and web services utilize them in their decision making process. Section 4 describes our experiments and results. Section 5 discussed relevant related work. Finally Section 6, concludes the paper and identifies future work.

@@

\section{Preliminaries}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations. Each row shows the gain the community can achieve by collaborating with other 5 communities. In this example for community $\textless 348 \textgreater$ we have: \\
$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
